CODECHECK: An open-science initiative for the independent execution of computations underlying research articles

### 2021-01-12 codecheck-paper.tex
final acks confirmation

\usepackage{booktabs}
\usepackage{doi} % turn DOIs into links
\usepackage{nameref}

@@

\begin{document}
\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles.}
\author[1,$\ast$]{Daniel N\"{u}st}
\author[2,$\ast$]{Stephen J Eglen}
\affil[1]{\url{https://orcid.org/0000-0002-0024-5046}}
\affil[2]{\url{https://orcid.org/0000-0001-8607-8025}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}}
\maketitle
\begin{abstract}
  This is a draft paper that we hope to submit to F1000R (and perhaps
  as a preprint before) in the coming weeks.
  \ldots{}
\end{abstract}

@@

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (GigaScience), and Andrew Hufton? (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang developed code and example certificates.
We thank Antonio P\'{a}ez (Journal of Geographical Systems) for enabling
CODECHECKs, Carlos Granell and Frank Ostermann for contributing
certificates as reproducibility reviewers at the AGILE conference, and 
all authors of auditable workflows for their participation.

>>>>

\usepackage{booktabs}
\usepackage{doi} % turn DOIs into links

@@

\begin{document}
\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles}
\author[1,$\ast$]{Daniel N\"{u}st}
\author[2,$\ast$]{Stephen J Eglen}
\affil[1]{\url{https://orcid.org/0000-0002-0024-5046}}
\affil[2]{\url{https://orcid.org/0000-0001-8607-8025}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}}
\maketitle
\begin{abstract}
  This is a draft paper that we hope to submit to F1000R (and perhaps
  as a preprint before) in the coming weeks.
  \ldots{}
\end{abstract}

@@

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (GigaScience), and Andrew Hufton (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang developed code and example certificates.
We thank Antonio P\'{a}ez (Journal of Geographical Systems) for enabling
CODECHECKs, Carlos Granell and Frank Ostermann for contributing
certificates as reproducibility reviewers at the AGILE conference, and 
all authors of auditable workflows for their participation.
